pema application

### 2022-11-23 paper/action_letter.Rmd
add supplemental tables

---
title       : "Selecting relevant moderators with Bayesian regularized meta-regression"
authors     : "masked"
journal     : "Research Synthesis Methods"
editor      : "Pigott"
manuscript  : "RSM-04-2022-0056"
class       : "draft"
bibliography      : ["r-references.bib", "references.bib",
                     "sara-references.bib", "eli-references.bib"]
output      : papaja::revision_letter_pdf
---

@@

@@

We appreciate the suggestion and have made the requested change. The Abstract now reads:

@@

In the Introduction, we now write:

REF

@@

REF

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

\RC{More in general, I do not like to see a mixture of methodology and R code. I think I would be more useful for  the reader to have sections describing the proposed approach and the underlying methodology (something that is not present at the emano) and then having an appendix about the code. }

@@

@@

@@

@@

@@

@@

@@

\RC{lines 449-452 are not necessary as bias and variance are known concepts. However, in Tables I can see only bias, and not information about variance.}

@@

@@

@@

@@

>>>>

---
title       : "Selecting relevant moderators with Bayesian regularized meta-regression"
authors     : "masked"
journal     : "Research Synthesis Methods"
editor      : "Pigott"
manuscript  : "RSM-04-2022-0056"
class       : "draft"
bibliography      : ["r-references.bib", "references.bib",
                     "sara-references.bib", "eli-references.bib", "metaforest.bib"]
output      : papaja::revision_letter_pdf
---

@@

In addressing all comments below, we have added detail and elaboration in many places. We hope that this addresses this comment.

@@

To address this comment and others,
we have restructured the Introduction to be more to the point.
We still provide the same background information in a more abbreviated form at a later point.
With regard to the specific request to mention penalisation/LASSO/horseshoe priors in the Abstract and Introduction, we have made the following changes. The Abstract now reads:

@@

The Introduction now states:

`r get_revision("lassointroduction")`

@@

To address the 3d comment by Reviewer 2, we have included the following paragraph in the revision:

@@

To address this comment and others,
we have restructured the Introduction to be more to the point.
We still provide the same background information in a more abbreviated form at a later point.
We have elaborated on all the points that were raised by the Reviewers (see our responses to the other comments).

@@

We have attempted to clarify this section by invoking an additional reference and rewriting it as follows:

`r get_revision("theory")`

@@

To address this comment, we have made the following changes:

1) We have rewritten the opening paragraph to clearly state the problem addressed in this paper, and the proposed solution:

`r get_revision("openingparagraph")`

\WorkInProgress

@@

\WorkInProgress

@@

We have made the suggested change and now use the intercept $\beta_0$ in place of $\Theta$. We have also simplified the notation of the estimated population effect to $\hat{\beta_0}$.

@@

As requested, we have added this information. These sections now read:

`r get_revision("morepriors")`

<!-- Second, the frequentist LASSO shrinks some coefficients to be exactly zero, thereby performing automatic variable selection.  -->
<!-- This is not the case for its Bayesian counterpart, which always provides a continuous posterior probability distribution. -->
<!-- Variable selection is then performed by determining which parameters have a high probability density assigned to near-zero values. -->
<!-- Third, classical penalized regression approaches rely on optimization while the Bayesian framework generally relies on Markov Chain Monte Carlo (MCMC) sampling to obtain the posterior distribution. As a result, Bayesian estimation tends to be slower compared to classical estimation. -->

@@

We agree with the Reviewer that this information would be better positioned in another section.
To address this comment, we have restructured the paper; the information about priors is now incorporated into the *Bayesian estimation* section, and the *Implementation* section now exclusively relates to the `pema` R-package.

@@

We intended to explain that the regularizing horseshoe prior is an extension of the (normal) horseshoe prior. This was insufficiently clear.
To address this comment, we have written the following section:

`r get_revision("horseshoe")`

@@

We have rephrased this so that it is clearer that the formula explains how this is achieved. The section now reads:

`r get_revision("expectedmods")`

@@

We thank the Reviewer for pointing out that this statement raises more questions than it answers. To address this Reviewer comment, we have moved this statement to the Discussion and slightly rephrased it to clarify that it is supported by the results of the present study. It now reads:

`r get_revision("sensitivityanalysis")`

@@

We agree with the Reviewer that the writing in this section was too methodological. To address this comment, we have made two changes: This paragraph has been moved to the section on Bayesian estimation, and we have rewritten it as follows:

`r get_revision("intervals")`

\RC{More in general, I do not like to see a mixture of methodology and R code. I think I would be more useful for  the reader to have sections describing the proposed approach and the underlying methodology (something that is not present at the emano) and then having an appendix about the code.}

To address this comment, we have made a stricter separation between methodology and code. 
All references to code are now relegated to the Implementation section.

We do believe that there are advantages to having code in the paper and not in an appendix, as the intended readership for this paper consists of those who wish to conduct a Bayesian regularized meta-analysis. We hope that the current approach is an acceptable compromise.

@@

This section is important because omitting the intercept from the model has very different implications for penalized Bayesian meta-regression than for frequentist models (where the model is equivalent, regardless of whether the intercept is included or not).

To clarify this, we have rewritten this section to focus on the implications of including or excluding the intercept.
The line explaining *how* to include or exclude the intercept has been moved to the Implementation paragraph, consistent with the Reviewer's request to relegate code to a separate section:

`get_revision("intercept")`

@@

We respectfully believe that this comment is based on a misunderstanding of the procedure.
We do not split a finite sample into a training and testing set - 
we simulate data for both sets from the same known data generating model.
Each sample from this model is independent and identically distributed (IID).
The distinction between training and testing is thus arbitrary.
This is different from real data analyses, where the available dataset is finite, and training and testing data are drawn from that finite dataset - thus violating the assumption of IID.

In a real dataset, if one case has very unusual values (i.e., an outlier),
the model could be biased if this case ends up in the training data, and the performance metrics could be biased if this case ends up in the testing data.
In our simulation study, outliers have exactly equal probabilities of appearing in the training or testing data - and as we are not sampling from a finite dataset, the probability of having an outlier in the training data is independent from having one in the testing data.

Their effect on the estimated parameters is known as "Monte Carlo error" and averages out across replications of the simulation.

@@

We respectfully feel that it is important to define how we operationalized each outcome metric, and why we use it.
Unfortunately, we now realize that our explanation was not sufficiently clear. To address this comment, we have rewritten the explanation of our outcome metric, $R^2_{test}$. We hope that this revised explanation clarifies that this is **not** the basic indicator R2, but rather, a different type of R2 that is suitable for assessing overfitting:

`r get_revision("rsquared")`

Additionally,
the reason we do not use AIC or BIC is because these are comparative fit indices, only suitable for comparing a set of models; we have only a single model and AIC or BIC do not speak to the absolute fit of a single model.

The reason we do not use adjusted $R^2$ is because it is an approximation of $R^2_{test}$ but calculated on the training sample data.
Since we simulate data from a known true model,
we do not need to *estimate* $R^2_{test}$ - we can *calculate* it directly, based on a new sample.

@@

We have rephrased this as suggested.

@@

As these simulations are very computationally demanding,
and increasing the number of replications adds only marginal accuracy gains, we did indeed use 100 replications.
However, as per the Reviewer's request, we have increased this to 1000.

@@

Thank you for pointing out this omission; we have corrected it.

@@

We corrected this, and slightly rephrased the sentence for clarity.

\RC{lines 449-452 are not necessary as bias and variance are known concepts.}

We respectfully feel that it is prudent to define how all outcome metrics are operationalized.
Even though the general concepts of bias and variance may be known to most readers,
we cannot assume that they will know exactly how these are calculated in the context of this simulation study - particularly for the broad readership of a journal like Research Synthesis Methods.
See also our response to the comment about defining $R^2_{test}$

\RC{However, in Tables I can see only bias, and not information about variance.}

This is correct; we had not reported these statistics for two reasons:

1. Unlike bias, they must be computed on aggregate across replications of each simulation condition. This results in a strange situation where each condition has only one outcome value. But it is probably fine to interpret these effect sizes as descriptive statistics.
2. The differences between algorithms in variance of $\tau^2$ were negligible. We did not want to devote two tables to, essentially, a matrix of zeroes.

To address this comment, we now describe the results in the text, and provide the requested tables as online Supplements.

@@

We thank the Reviewer for pointing this out;
a fragment of a sentance was cut here.
We restored the original text.

@@

We have done as requested.

@@

This observation is correct, but this is not a problem. 
The method is validated for up to 100 studies,
so it should also be valid for >100 studies,
as a larger sample size gives more power.

The reason we used these data is because we were able to secure permission from the original author to include them in the R-package.
This means we can make the examples reproducible, requiring only the `pema` package.
We feel that it adds a lot to the paper to present a reproducible real-data example based on a novel dataset.
To address this comment,
we now acknowledge in the text that this sample is relatively large compared to the sample sizes of the simulation study:

\WorkInProgress

@@

We thank the Reviewer for their encouraging words and thought-provoking comments, which we feel have helped improve the quality of the manuscript.
